Demand-aware geo-distributed placement for low latency

### 2015-07-05 auspice/eval-case.tex
added shrink, auspice, first draft background, intro edited

@@

>>>>

\begin{figure*}[ht]
	\vspace{0.05in}
	\begin{minipage}[b]{0.48\linewidth}
		\centering
		\includegraphics[width=2.8in,height=1.4in]{graph/newgraphs/managed-lookup.pdf}
		\figvsp
		\caption{Lookup latency:  \auspice\ with 5 replicas is comparable to UltraDNS (16 replicas); \auspice\ with 15 replicas has 60\% lower latency than UltraDNS.}
		\label{fig:managed-lookup}
	\end{minipage}
	\hspace{0.2in}
	\begin{minipage}[b]{0.48\linewidth}
		\centering
		\includegraphics[width=2.8in,height=1.4in]{graph/newgraphs/managed-update.pdf}
		\figvsp
		\caption{Update propagation delay: \auspice\ with 5 replicas is  1.0 to 24.7 secs lower than three top-tier managed DNS service providers. }
		\label{fig:manageddnsupdate}
	\end{minipage}
	%\hspace{0.3cm}
	%\begin{minipage}[b]{0.3\linewidth}
	%\centering
	%\includegraphics[width=2in,height=1.5in]{graph/medianlatencyVSlocality.pdf}
	%\figvsp
	%\caption{[Simulator] Workload sensitivity: \auspice\ lowers latency by 2--5$\times$  over \staticthree\ at all geo-locality levels.}
	%\label{fig:varylocality}
	%\end{minipage}
	\vspace{-0.25in}
\end{figure*}

@@

\subsubsection{Time-to-connect to ``moving'' endpoints}
\label{sec:ttc_exp}

We evaluate the time-to-connect to a moving destination as a function of the mobility (or update) rate. The {\em end-to-end time-to-connect}  here is measured as the latency to look up an up-to-date address of the destination (or the time-to-connect as defined in $\S$\ref{sec:design_overview}) plus the time for msocket to successfully establish a TCP connection between the client and the mobile destination. This e2e-time-to-connect also incorporates the impact of timeouts and retried lookups if the client happens to have obtained a stale value (as in Fig. \ref{fig:4mobility}). The experiment is conducted on PlanetLab and consists of a single msocket client and a single mobile msocket server that is ``moving'' by changing its listening port number on a remote machine, and updating the name record replicated on three \auspice\ name servers accordingly. 
A successful connection setup delay using msocket is takes 2 RTTs (2 $\times$ 105 ms)  \cite{msocketTR}. 
As defined in Eq. \ref{eq:ttc}, the values of the update propagation latency $d_i$ and the lookup latency $l_i$ are 250 ms and 20 ms respectively, and the update rate $w_i$ varies from 1/1024/s to 1/s.
The timeout value ($T$) in our experiment is dependent on the RTT between the client and the server. If the client attempts to connect to the server on a port which the server is not listening on, the server immediately returns an error response to the client. Specifically, the timeout value is either 1 or 2 RTTs with equal probability depending on whether the connection failed during the first or the second round-trip of msocket's connection setup.
The client sends lookups at a rate of 10/s (but this rate does not affect the time-to-connect), and both lookups and updates inter-arrival times are exponentially distributed.

Figure \ref{fig:ttc_msocket} shows the distribution of the time-to-connect with update propagation delays entailed by eventual consistency. For low-to-moderate mobility rates ($<\frac{1}{64s}$), we find that all time-to-connect values are close to 230 ms, of which 20ms is the lookup latency, and 210ms is msocket's connection setup latency. The reason the client is able to obtain the correct value upon first lookup in all cases is that the update propagation latency of 250ms is much smaller than the average inter-update interval (64s).  The update propagation delay becomes a non-trivial fraction of the inter-update interval at high mobility rates of $\approx$1/sec that results in  26\% of lookups returning stale values. The mean e2e-time-to-connect increases to  302 ms for an update rate of 1/sec, which suggests that \auspice's time-to-connect is limited by network propagation delays in this regime. Nevertheless, once a connection is successfully established, {individual} migration can quickly resynchronize the connection in $\approx$two round-trips between the client and the mobile without relying on \auspice\ (not shown here). 
%A different experiment with totally ordered writes shows qualitatively similar conclusions \cite{techreport}.

Figure \ref{fig:ttc_msocket} also shows that the time-to-connect as predicted by our analytical model (Eq. \ref{eq:ttc}) are close to those observed in the experiment, thereby re-affirming our design.

%\blue{We evaluate the time-to-connect to a moving destination as a function of the mobility (or update) rate. We stick with the running definition of time-to-connect used in the paper, namely, the time to look up an up-to-date address of the destination, i.e., an address to which the client can successfully establish a TCP connection. This definition excludes the (successful) connection setup delay itself as that delay is independent of \auspice's design, but it does incorporate the impact of timeouts and retried lookups if the client happens to have obtained a stale value (as in Fig. \ref{fig:4mobility}). The experiment is conducted on PlanetLab and consists of a single virtual client and a single virtual mobile server that is ``moving'' by changing its listening port number on a remote machine, and updating the name record replicated on three \auspice\ name servers accordingly. As defined in Eq. \ref{eq:ttc}, the values of the timeout $T_i$ and lookup latency $l_i$ are 5 secs and 50 ms respectively, and the update rate $w_i$ varies from $10^{-4}$/s to 1/s. The client sends lookups at a rate of 10/s (but this rate does not affect the time-to-connect), and both lookup and update inter-arrival times are exponentially distributed}

%\blue{Figure \ref{fig:ttc} shows the distribution of the time-to-connect with update propagation delays entailed by eventual consistency. For low-to-moderate mobility rates ($< 0.01/$s), we find that all lookup latencies are much smaller than 5 sec and mean time-to-connect is less than 50 ms, i.e.,  the client is able to obtain the correct value upon first lookup in all cases. This is because the update propagation latency of 190 ms is much smaller than the average inter-update interval (100 s).  The update propagation delay becomes a non-trivial fraction of the inter-update interval at high mobility rates of 0.1 to 1/sec that respectively result in 1.5\% and 13\% of timeouts for lookups. The mean time-to-connect increases to  641 ms for an update rate of 1/sec, which suggests that \auspice's time-to-connect is limited by network propagation delays in this regime. Nevertheless, once a connection is successfully established, {individual} migration can quickly resynchronize the connection in about two round-trips between the client and the mobile without relying on \auspice\ (not shown here). %A different experiment with totally ordered writes shows qualitatively similar conclusions \cite{techreport}.}

%\blue{Figure \ref{fig:ttc} also shows that the time-to-connect as predicted by our analytical model (Eq. \ref{eq:ttc}) is close to those observed in the experiment, thereby re-affirming our design. }

\eat {
	% sequential single-column figures

	\begin{figure}[ht]
		\vsp
		\centering
		\includegraphics[width=3in, height=1.5in]{figure/SimulMig.pdf}
		\figvsp
		\caption{Simultaneous mobility recovery in $\approx$2 RTTs after both endpoints resurface.}
		\label{fig:SimulMig}
	\end{figure}

	\begin{figure}[ht]
		\figvsp
		\centering
		\includegraphics[width=2in, height=1.5in]{figure/5MemTimeLineUsed.pdf}
		\figvsp
		\caption{Context-aware delivery timeline showing 3 messages being geo-cast to 5 members.}
		\label{fig:5MemberTimeline}
		\figvsp
	\end{figure}
}

\subsubsection{Simultaneous endpoint mobility}

Figure \ref{fig:SimulMig} shows an experiment involving simultaneous mobility. The client is an Android phone using \msocket\ via a WiFi interface to connect to a publicly addressable Planetlab machine at time 0. The server and client shut down their interfaces respectively around 15 and 20 sec. Subsequently, the server restarts its interface and starts listening on a different port and updates \auspice\ accordingly. After that, the client restarts its interface and attempts to re-synchronize the connection. This re-synchronization time is roughly 300ms as shown and consists of the following delays. The client performs a query to \auspice\ to resolve the server's GUID to its new socket address (IP, port), which takes roughly 50ms and mostly corresponds to the round-trip delay between the client and the \auspice\ nameserver. The remaining 250ms roughly correspond to 2 RTTs of delay between the client and the server that are separated by a round-trip delay of 120ms.

\subsubsection{Context-aware delivery}
\label{sec:context}

Next, we show a proof of concept of context-aware communication, a novel communication primitive enabled by \auspice's extensible key-value API. \auspice\ allows applications to bind an \msocket\ not only to human-readable names or GUIDs, but also to abstract context descriptors as in \verb+msocket.bind("[geoloc: [lat,long],radius]")+.  Writes to this \msocket\ are reliably delivered to all GUIDs in the geo-fence created by this descriptor. Underneath the covers, \msocket\ invokes \auspice\ to create on-demand a {group GUID}, i.e., a  GUID with a membership field consisting of a set of member GUIDs, and obtains this member set. \msocket\ internally resolves each member GUID to its socket address and establishes an \msocket\ connection for reliably delivery.

Figure \ref{fig:5MemberTimeline} shows an experiment involving a group creator (also the message sender) on an Android phone and a number of potential members on PlanetLab nodes, 5 of which fake-register their coordinates in \auspice\ so as to appear to be within the created geo-fence. The RTT between the group creator and members is 125ms. The figure shows that group creation, a single call to \auspice\ that returns all member GUIDs, takes roughly 200ms. Subsequently, an internal \msocket\ connect to each member involves another \auspice\ lookup to resolve the GUID to a socket address and connect in parallel to all 5 members, which takes 250-280ms. After this, the creator sends 3 short messages back-to-back that each take roughly 1 RTT to be reliably delivered.

%Context-aware group GUIDs in \auspice\ are active, i.e., \auspice\ refreshes the membership set periodically so that if an existing member leaves or a new member arrives into the context-space, the group GUID is updated accordingly. This refresh interval limits how responsive context-aware communication is to member churn. 
More details of optimizing context-aware queries in \auspice, reducing membership staleness, the connection migration protocol, etc. are outside the scope of this paper \cite{msocketTR}. This experiment seeks only to exemplify a powerful, new communication primitive enabled by context descriptors compared to strictly hierarchical DNS names, as argued in $\S$\ref{sec:whyNotDNS}.

### 2015-07-05 auspice/eval-part2.tex
added shrink, auspice, first draft background, intro edited

\begin{figure*}[ht]
\vspace{0.05in}
\begin{minipage}[b]{0.48\linewidth}
\centering
\includegraphics[scale=0.55]{graph/newgraphs/managed-lookup.pdf}
\figvsp
\caption{Lookup latency:  \auspice\ with 5 replicas is comparable to UltraDNS (16 replicas); \auspice\ with 15 replicas has 60\% lower latency than UltraDNS.}
\label{fig:managed-lookup}
\end{minipage}
\hspace{0.2in}
\begin{minipage}[b]{0.48\linewidth}
\centering
\includegraphics[scale=0.55]{graph/newgraphs/managed-update.pdf}
\figvsp
\caption{Update propagation delay: \auspice\ with 5 replicas is  1.0 to 24.7 secs lower than three top-tier managed DNS service providers. }
\label{fig:manageddnsupdate}
\end{minipage}
%\hspace{0.3cm}
%\begin{minipage}[b]{0.3\linewidth}
%\centering
%\includegraphics[width=2in,height=1.5in]{graph/medianlatencyVSlocality.pdf}
%\figvsp
%\caption{[Simulator] Workload sensitivity: \auspice\ lowers latency by 2--5$\times$  over \staticthree\ at all geo-locality levels.}
%\label{fig:varylocality}
%\end{minipage}
\vspace{-0.25in}
\end{figure*}

@@

\subsection{Sensitivity analyses and other results.} 
\label{sec:other} 
We have conducted a comprehensive evaluation of the sensitivity of \auspice's performance-cost trade-offs to workload and system parameters across scales varying by several orders of magnitude. These include workload parameters such as geo-locality, read-to-write rate ratio, ratio of device-to-service names, etc. and system parameters such as the fault-tolerance threshold, capacity utilization, perturbation knob, the tunable overhead of replica reconfiguration, etc. using a combination of simulation and system experiments. These results do not qualitatively change the above findings, and are deferred to the technical report \cite{techreport}.

>>>>

%!TEX root = Main.tex

@@

\vspace{-0.1in}
{\paragraph{Sensitivity analyses and other results}} \label{sec:other} We have conducted a comprehensive evaluation of the sensitivity of \auspice's performance-cost trade-offs to workload and system parameters across scales varying by several orders of magnitude. These include workload parameters such as geo-locality, read-to-write rate ratio, ratio of device-to-service names, etc. and system parameters such as the fault-tolerance threshold, capacity utilization, perturbation knob, the tunable overhead of replica reconfiguration, etc. using a combination of simulation and system experiments. These results do not qualitatively change the findings in this paper, and are deferred to the technical report \cite{techreport}.

### 2015-07-05 auspice/eval.tex
added shrink, auspice, first draft background, intro edited

\section{Evaluation}
\label{sec:eval}

Our evaluation is centered around an representative application: a global name service (GNS) to provide name-to-address mapping for mobile devices. 
We expect a GNS to  receive requests from clients spread in a large geographic area and the records in GNS to show a non-trivial update rate due to end-host mobility. These traits make a GNS a representative application for \auspice. In the following discussion, we refer an \auspice\ server as a \emph{name server}, an Auspice client as a \emph{local name server}, and a record as a \emph{name record} or a \emph{name}.

Our evaluation seeks to answer the following questions: (1) How well does \auspice's design meet its performance, cost, and availability goals compared to state-of-the-art alternatives under high mobility? (2) How does \auspice's cost-performance tradeoff compare to best-of-breed managed DNS services for today's (hardly mobile) domain name workloads?

@@

\vspace{-0.1in}
\subsection{Experimental setup}

\textbf{Testbeds:} We use geo-distributed testbeds (Amazon EC2 or Planetlab) or local emulation clusters (EC2 or a departmental cluster) depending upon the experiment's goals.

@@

The following are default experimental parameters for {\em device names}. The ratio of the total number of lookups across all devices to the total number of updates is 1:1, i.e., devices are queried for on average as often as they change addresses. The lookup rate of any single device name is uniformly distributed between 0.5--1.5$\times$ the average lookup rate; the update rate is similarly distributed and drawn independently.%, so there is no correlation between the lookup and update rate of a name.

\begin{table}[t]
\centering
\small{
\begin{tabular}{c|c}
{\bf Workload parameter} & {\bf Value} \\ \hline
Fraction of (highly mobile) device names & 90\%  \\ \hline
Fraction of (mostly static) service names & 10\%   \\ \hline
\% of device name lookups   & 33.33\%  \\ \hline
\% of device name updates  & 33.33\% \\ \hline
\% of service name lookups   & 33.33\%  \\ \hline
\% of service name updates  & 0.01\% \\ \hline
Geo-locality: [devices, services] & [0.75, 0.8]  \\ \hline
\end{tabular}
}
\caption{Default workload parameters. %(except $\S$\ref{sec:sensitivity}).
}
\vspace{-0.15in}
\label{tab:setup}
\end{table}

@@

Table \ref{tab:setup} summarizes the default workload parameters.

@@

@@

We conduct experiments in this subsection on a 16-node (each with Xeon 5140, 4-cores, 8 GB RAM) departmental cluster, wherein each machine hosts 10 instances of either name servers or local name servers so as to emulate an 80-name server \auspice\ deployment. We instrument the instances so as to emulate wide-area latencies between any two instances that correspond to 160 randomly chosen Planetlab nodes. We choose emulation instead of a geo-distributed testbed in this experiment in order to obtain reproducible results while stress-testing the load-vs.-response time scaling behavior of various schemes given identical resources.

@@

\begin{figure*}[t]
\centering
\subfigure[Lookup latencies (load = 0.3)]{\label{fig:namesquerymediancdf}\includegraphics[scale=0.55]{graph/newgraphs/lookup-latency-cdf.pdf}}
\subfigure[Lookup latency vs. load]{\label{fig:load}\includegraphics[scale=0.55]{graph/newgraphs/load-latency.pdf}}
\subfigure[Update cost vs. load]{\label{fig:loadupdatecost}\includegraphics[scale=0.55]{graph/newgraphs/load-updatecost.pdf}}
\subfigure[Update latency]{\label{fig:updates}\includegraphics[scale=0.55]{graph/newgraphs/update-latency-cdf.pdf}}
\caption{\small{\auspice\ has up to 5.7$\times$ to 9$\times$ lower latencies than \staticthree\ and \codons\ reps. (\ref{fig:load}). A load of 1 means 200 lookups/sec and 100 updates/sec per name server. \replicateall\ peaks out at a load of 0.3 while \auspice\ can sustain a request load of up to 8 as it carefully chooses between 3 and 80 replicas per name. In Figure \ref{fig:updates}, median update latency of \auspice\ with total write ordering per name is 284ms and is comparable to other  schemes.}}
\vspace{-0.15in}
\label{fig:lookupupdate}
\end{figure*}

@@

@@

%\subfigure{\label{fig:updatelatency}\includegraphics[scale=0.55]{graph/newgraphs/}}

@@

The {\em update propagation delay}, i.e., the time from when a client issued a write till the last replica executes the write, is a key determiner of the time-to-connect. With eventual consistency, update propagation takes one round, while with total write ordering, update propagation takes two rounds and 50\% more messages.

@@

\subsubsection{Time-to-connect to ``moving'' endpoints}
\label{sec:ttc_exp}

We evaluate the time-to-connect to a moving destination as a function of the mobility (or update) rate.  This experiment is performed with the help of \msocket\ \cite{msocketTR}, a user-level socket library that interoperates with \auspice.  The {\em end-to-end time-to-connect}  here is measured as the latency to look up an up-to-date address of the destination (or the time-to-connect as defined in $\S$\ref{sec:design_overview}) plus the time for msocket to successfully establish a TCP connection between the client and the mobile destination. This e2e-time-to-connect also incorporates the impact of timeouts and retried lookups if the client happens to have obtained a stale value.

The experiment is conducted on PlanetLab and consists of a single msocket client and a single mobile msocket server that is ``moving'' by changing its listening port number on a remote machine, and updating the name record replicated on three \auspice\ name servers accordingly.  A successful connection setup delay using msocket is takes 2 RTTs (2 $\times$ 105 ms)  \cite{msocketTR}.  The values of the update propagation latency $d_i$ and the lookup latency $l_i$ are 250 ms and 20 ms respectively, and the update rate $w_i$ varies from 1/1024/s to 1/s. The timeout value ($T$) in our experiment is dependent on the RTT between the client and the server. If the client attempts to connect to the server on a port which the server is not listening on, the server immediately returns an error response to the client. Specifically, the timeout value is either 1 or 2 RTTs with equal probability depending on whether the connection failed during the first or the second round-trip of msocket's connection setup.
The client sends lookups at a rate of 10/s (but this rate does not affect the time-to-connect), and both lookups and updates inter-arrival times are exponentially distributed.

Figure \ref{fig:ttc} shows the distribution of the time-to-connect with update propagation delays entailed by eventual consistency. For low-to-moderate mobility rates ($<\frac{1}{64s}$), we find that all time-to-connect values are close to 230 ms, of which 20ms is the lookup latency, and 210ms is msocket's connection setup latency. The reason the client is able to obtain the correct value upon first lookup in all cases is that the update propagation latency of 250ms is much smaller than the average inter-update interval (64s).  The update propagation delay becomes a non-trivial fraction of the inter-update interval at high mobility rates of $\approx$1/sec that results in  26\% of lookups returning stale values. The mean e2e-time-to-connect increases to  302 ms for an update rate of 1/sec, which suggests that \auspice's time-to-connect is limited by network propagation delays in this regime. Nevertheless, once a connection is successfully established, {individual} migration can quickly resynchronize the connection in $\approx$two round-trips between the client and the mobile without relying on \auspice\ (not shown here). 
%A different experiment with totally ordered writes shows qualitatively similar conclusions \cite{techreport}.

We have also developed an analytical model to predict time-to-connect values \cite{techreport}. Figure \ref{fig:ttc} also shows that the time-to-connect as predicted by our analytical model are close to those observed in the experiment, thereby re-affirming our design.

\begin{figure*}[t]
\begin{minipage}[b]{0.48\linewidth}
\centering
\includegraphics[scale=0.55]{graph/camera-ready/connect-time-msocket.pdf}
\caption{Time-to-connect $\approx$ lookup latency for moderate mobility rates ($<$1/100s)  as \auspice\ returns up-to-date responses w.h.p., but sharply rises thereafter.}
\label{fig:ttc}
\end{minipage}
\hspace{0.3cm}
\begin{minipage}[b]{0.48\linewidth}
\centering
\includegraphics[scale=0.55]{graph/camera-ready/latency_by_time.pdf}
\caption{\auspice\ adapts to varying demand geo-locality in two epochs each 75s long with a (tunable) reconfiguration message overhead of 3.6\%.}
\label{fig:latency-time}
\end{minipage}
%\vspace{-0.25in}
\end{figure*}
% Box plot shows min, 5th \%-ile, median, 95th \%-ile, and max. Asterisk shows the mean.

\subsubsection{Reconfiguration overhead vs. responsiveness}

@@

\blue{
We show the lookup latencies of \auspice\ and the message overhead of reconfiguration in the experiment in Figue \ref{fig:latency-time}.   We find that \auspice\ takes two epochs to infer a change in the geo-distribution of demand and to adapt to it.  This result suggests that \auspice\ can optimize lookup latencies provided the geo-distribution of demand for a name remains stable for a few epochs.
Further, we measured the overhead of reconfiguration messages in this experiment to be 3.6\%. The overhead is less than the expected overhead of 10\% because not all names are reconfigured in every epoch. 
%This finding shows that choosing epoch lengths as per the analysis in  Section \ref{sec:gc-analysis} keeps the overhead of group changes to a small fraction of the overall system load.
}

>>>>

%!TEX root = Main.tex
\section{Evaluation}
\label{sec:eval}

Our evaluation seeks to answer the following questions: (1) How well does \auspice's design meet its performance, cost, and availability goals compared to state-of-the-art alternatives under high mobility? (2) Can \auspice\ serve as a complete, end-to-end solution for mobility and enable novel communication abstractions? (3) How does \auspice's cost-performance tradeoff compare to best-of-breed managed DNS services for today's (hardly mobile) domain name workloads?

%Our main goal is to quantify the benefits and costs of the choices in \auspice's distributed design---our main contribution---with respect to the subset of design goals  ($\S$\ref{sec:design_goals}) that are quantifiable, namely client-perceived latency benefit and provider-perceived update cost under high mobility. We use the implemented prototype to evaluate (1) \auspice's replication strategies against simple ones used by DNS providers today as well as DHT-based alternatives proposed in research, and (2) a deployment of \auspice\ against several commercial managed DNS providers in live operation. We use simulations to evaluate (3) the sensitivity of \auspice's benefits with respect to mobile workload parameters, and (4) the scalability of \auspice\ to regimes beyond those permitted by our testbeds. We do not attempt to evaluate \auspice's functional design goals---resilience to failures, consistency, extensibility, security---except to the extent that all experiments subsume the overhead of these features.

@@

\vspace{-0.1in}
\subsection{Experimental setup}
%We first evaluate the latency and cost benefits of \auspice's demand-aware placement against static placement schemes. %and (2) the scalability of \auspice\ with the number of names over several orders of magnitude.
%\subsubsection{Experiment setup}

\textbf{Testbeds:} We use geo-distributed testbeds (Amazon EC2 or Planetlab) or local emulation clusters (EC2 or a departmental cluster) depending upon the experiment's goals. %The departmental cluster consists of 16 machines  (Xeon 5140, 4-core, 8 GB RAM)  and the EC2 instances are ``m3.xlarge" with 15GB RAM. %\tbd{Emulab.}

@@

%A vexing evaluation  challenge is that we do not have a workload of clients querying a name service in order to communicate with mobile devices moving across different network addresses. There is no global name resolution infrastructure for mobile device names today and most mobile devices do not have publicly visible addresses, so no one queries for them.

The following are default experimental parameters %(except for $\S$\ref{sec:sensitivity} on sensitivity analysis) 
for {\em device names}. The ratio of the total number of lookups across all devices to the total number of updates is 1:1, i.e., devices are queried for on average as often as they change addresses. The lookup rate of any single device name is uniformly distributed between 0.5--1.5$\times$ the average lookup rate; the update rate is similarly distributed and drawn independently.%, so there is no correlation between the lookup and update rate of a name.

\rmCR{
\begin{table}[t]
\centering
\small{
\begin{tabular}{c|c}
{\bf Workload parameter} & {\bf Value} \\ \hline
Fraction of (highly mobile) device names & 90\%  \\ \hline
Fraction of (mostly static) service names & 10\%   \\ \hline
\% of device name lookups   & 33.33\%  \\ \hline
\% of device name updates  & 33.33\% \\ \hline
\% of service name lookups   & 33.33\%  \\ \hline
\% of service name updates  & 0.01\% \\ \hline
Geo-locality: [devices, services] & [0.75, 0.8]  \\ \hline
\end{tabular}
}
\caption{Default workload parameters. %(except $\S$\ref{sec:sensitivity}).
}
\vspace{-0.15in}
\label{tab:setup}
\end{table}
}

\begin{figure*}[t]
\subfigure[Lookup latencies (load = 0.3)]{\label{fig:namesquerymediancdf}\includegraphics[scale=0.55]{graph/newgraphs/lookup-latency-cdf.pdf}}
\subfigure[Lookup latency vs. load]{\label{fig:load}\includegraphics[scale=0.55]{graph/newgraphs/load-latency.pdf}}
\subfigure[Update cost vs. load]{\label{fig:loadupdatecost}\includegraphics[scale=0.55]{graph/newgraphs/load-updatecost.pdf}}
%\subfigure[Update cost]{\label{fig:updatebw}\includegraphics[scale=0.55]{graph/newgraphs/cdf-update-cost.pdf}}
\vspace{-0.15in}
\caption{\small{\auspice\ has up to 5.7$\times$ to 9$\times$ lower latencies than \staticthree\ and \codons\ reps. (\ref{fig:load}). A load of 1 means 200 lookups/sec and 100 updates/sec per name server. \replicateall\ peaks out at a load of 0.3 while \auspice\ can sustain a request load of up to 8 as it carefully chooses between 3 and 80 replicas per name.}}
\vspace{-0.15in}
\label{fig:lookupupdate}
\end{figure*}

@@

%Table \ref{tab:setup} summarizes the default workload parameters.

@@

\eat {
\begin{figure*}[t]
\vspace{0.05in}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.55]{graph/newgraphs/update-latency-cdf.pdf}
\caption{Median update latency of \auspice\ with total write ordering per name is 284ms and is comparable to other  schemes. } 
\label{fig:updates}
\end{minipage}
\hspace{0.3cm}
\begin{minipage}[b]{0.35\linewidth}
\centering
\includegraphics[scale=0.55]{graph/camera-ready/connect-time-eventual.pdf}
\caption{Time-to-connect $\approx$ lookup latency for moderate mobility rates ($<$1/100s)  as \auspice\ returns up-to-date responses w.h.p., but sharply rises thereafter (as per Eq. \ref{eq:ttc}).}
\label{fig:ttc}
\end{minipage}
\hspace{0.3cm}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.55]{graph/camera-ready/latency_by_time.pdf}
\caption{\auspice\ adapts to varying demand geo-locality in two epochs each 75s long with a (tunable) reconfiguration message overhead of 3.6\%.}
\label{fig:latency-time}
\end{minipage}
%\vspace{-0.25in}
\end{figure*}
% Box plot shows min, 5th \%-ile, median, 95th \%-ile, and max. Asterisk shows the mean.
}

@@

We conduct experiments in this subsection on a 16-node (each with Xeon 5140, 4-cores, 8 GB RAM) departmental cluster, wherein each machine hosts 10 instances of either nameservers or local nameservers so as to emulate an 80-nameserver \auspice\ deployment. We instrument the instances so as to emulate wide-area latencies between any two instances that correspond to 160 randomly chosen Planetlab nodes. We choose emulation instead of a geo-distributed testbed in this experiment in order to obtain reproducible results while stress-testing the load-vs.-response time scaling behavior of various schemes given identical resources.

@@

@@

\begin{figure*}[t]
\subfigure[E2E time-to-connect]{\label{fig:ttc_msocket}\includegraphics[width=2.4in,height=1.8in]{graph/camera-ready/connect-time-msocket.pdf}}
\subfigure[Simultaneous mobility]{\label{fig:SimulMig}\includegraphics[width=2.5in, height=1.8in]{figure/SimulMig.pdf}}
\subfigure[Context-aware delivery]{\label{fig:5MemberTimeline}\includegraphics[width=2in, height=1.8in]{figure/5MemTimeLineUsed.pdf}}
\vspace{-0.2in}
\caption{(a) Time-to-connect$\approx$lookup latency for moderate mobility rates ($<\frac{1}{10s}$)  as \auspice\ returns up-to-date responses w.h.p., but sharply rises thereafter (Eq. \ref{eq:ttc}); (b) Simultaneous mobility recovery in $\approx$2 RTTs after both endpoints resurface; (c) Context-aware delivery showing 3 messages  geo-cast to 5 members.}
\vspace{-0.1in}
\label{fig:end2end}
\end{figure*}

@@

\eat{
\begin{figure}[h]
\centering
\includegraphics[scale=0.55]{graph/newgraphs/update-latency-cdf.pdf}
%\includegraphics[scale=0.55]{graph/system-exp/cdf-names-median-update.pdf}
\vspace{-0.2in}
\caption{[System] Median update latency of \auspice\ is 284ms and is comparable to those of other schemes.} 
%The high latencies for \replicateall\ are because of insufficient upload capacity on PlanetLab.}
\label{fig:updates}
\vspace{-0.1in}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.55]{graph/newgraphs/managed-update.pdf}
\vspace{-0.1in}
\caption{Median  update latency of \auspice\ for updating replicas at 5 locations is  1.0 sec to 24.7 sec lower than three managed DNS providers. Values shown are 5, 25, 50, 75,  and 95 percentiles.}
\vspace{-0.2in}
\label{fig:manageddnsupdate}
\end{figure}

\begin{figure}[t]
\includegraphics[scale=0.5]{graph/medianlatencyVSlocality.pdf}
\vspace{-0.1in}
\caption{[Simulator] Workload sensitivity. \auspice\ gives 2$\times$ to 5$\times$  lower latencies across all locality levels.}
\label{fig:varylocality}
\vspace{-0.1in}
\end{figure}

}
%\subfigure{\label{fig:updatelatency}\includegraphics[scale=0.55]{graph/newgraphs/}}

@@

The {\em update propagation delay}, i.e., the time from when a client issued a write till the last replica executes the write, is a key determiner of the time-to-connect. As shown in $\S$\ref{sec:scalability}, with eventual consistency, update propagation takes one round, while with total write ordering, update propagation takes two rounds and 50\% more messages.

@@

\eat {
\begin{figure}[t]
\vsp
\centering
\includegraphics[width=2.4in,height=1.5in]{graph/camera-ready/connect-time-eventual.pdf}
\figvsp
\caption{Time-to-connect $\approx$ lookup latency for moderate mobility rates ($<$1/100s)  as \auspice\ returns up-to-date responses w.h.p., but sharply rises thereafter (as per Eq. \ref{eq:ttc}).}
\label{fig:ttc}
\figvsp
\end{figure}
}

%The time-to-connect to a mobile name for a client is the sum of the time to get the correct address of the mobile and the TCP connection setup latency. As the latter latency is independent of the \auspice's design, we measure the former latency.  Our experiment setup on PlanetLab consists of a single (virtual) client and a single (virtual) mobile co-located with distinct local name servers.  The mobile's name record is stored on three name servers, and is updated by the mobile during an experiment. The client reads the mobile's  name record from \auspice\ and  verifies if the value in the name record is correct by establishing a TCP connection to the mobile on a fixed address.  On an incorrect response, the client retries the lookup after a timeout of 5 sec.  We run five experiments of 10 min each by varying the update rate of the mobile from 0.0001 updates/s to 1 update/s; the client sends  lookup at a rate of 10/sec in each case. The inter-arrival times between lookups (updates) follow an exponential distribution. 
%\tbd{We have also validated that the time-to-connect observed using msocket yields values close to this observed in the experiment above.}

%This model, included in our tech report \cite{techreport}, calculates time-to-connect $C$ as a function of lookup latency $l$, update latency $u$, update rate $r$, and connect-timeout $T$ as follows: $C = l + (1-e^{-r u})(l + T)/e^{-r u}$.   In Figure \ref{fig:ttc}, the time-to-connect values predicted by the model are comparable to actual mean time-to-connect values across all update rates, which further validates our findings.  Overall, our results show that for expected mobility rates Auspice returns correct responses on first lookup with high probability, thereby ensuring low time-to-connect for clients.

%\subsubsection{Choosing group change epoch length}
%\label{sec:gc-analysis}
%\auspice\ chooses group length epochs so that the overhead of group changes is a small fraction of overall load and the system is responsive to changes in demand geo-distribution.  First, we quantify the message overhead for a group change of a single name. We denote number of replica controllers by $M$, and the number of old (new) replicas by $r_1$ ($r_2)$.  Note that ordering a single request via paxos uses $cn$ messages, where $n$ is the number of replicas and c (= 3) is a constant.  The message overhead of each step in group change is as follows: (1) replica controllers agreeing to a new set of replicas = $cM$ (2) old active replicas stopping their paxos instance = $cr_1$ (3) informing new active replicas of reconfiguration = $2r_2$ (4) replica controllers agreeing that group change is complete = $cM$.  Next, we quantify the total rate of messages due to read and write requests in the system for the case of totally ordered writes. The total message rate is equal to $\sum_i (r_i + c n_i w_i)$, where  $r_i$, $w_i$, and $n_i$ are respectively the read rate, the write rate, and the current number of replicas for name $i$.

%To limit the overhead of reconfiguration to say 5\%, the epoch length is set to (group change overhead for all names)/(total rate of read and write messages)/5\%.  To account for the fact that only a fraction of names may be reconfigured in an epoch, we multiply the epoch length $T$ by the expected fraction of names that may be reconfigured. We assume that the expected fraction is equal to the fraction of names reconfigured in the previous epoch.  In our implementation, each node first independently calculates an epoch length based on statistics for names stored at that node, and broadcasts it to all other nodes once in each epoch. Finally, the epoch length is chosen by taking the average of epoch length of all nodes.

\rmCR{
\subsubsection{Reconfiguration overhead vs. responsiveness}

@@

\blue{
We show the lookup latencies of \auspice\ and the message overhead of reconfiguration in the experiment in Figue \ref{fig:latency-time}.   We find that \auspice\ takes two epochs to infer a change in the geo-distribution of demand and to adapt to it.  This result suggests that \auspice\ can optimize lookup latencies provided the geo-distribution of demand for a name remains stable for a few epochs.
Further, we measured the overhead of reconfiguration messages in this experiment to be 3.6\%. The overhead is less than the expected overhead of 10\% because not all names are reconfigured in every epoch. 
%This finding shows that choosing epoch lengths as per the analysis in  Section \ref{sec:gc-analysis} keeps the overhead of group changes to a small fraction of the overall system load.
}
}
